R tools for accessing research literature for text mining

### 2019-05-06 manuscript.Rmd
Typo

There's more than 100 million research articles published
(Crossref API: <https://github.com/CrossRef/rest-api-doc>), representing
an enormous amount of knowledge. In addition to simply reading these
articles, the articles contain a vast trove of information of interest to
researchers for machine aided questions [@Kong2018; @Usai2018]. For example,
many researchers are interested in statistical outcomes of articles that 
can be extracted from numeric results: P-values, effect sizes, means, and
more. In addition, researchers are often interested in words in articles,
their use through time, and the contexts they are found in.

>>>>

There are more than 100 million research articles published
(Crossref API: <https://github.com/CrossRef/rest-api-doc>), representing
an enormous amount of knowledge. In addition to simply reading these
articles, the articles contain a vast trove of information of interest to
researchers for machine aided questions [@Kong2018; @Usai2018]. For example,
many researchers are interested in statistical outcomes of articles that 
can be extracted from numeric results: P-values, effect sizes, means, and
more. In addition, researchers are often interested in words in articles,
their use through time, and the contexts they are found in.
